Creating optimal conditions for reproducible data analysis in \R with `fertile'\protect\thanks{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the \pkg{tidyverse} team.}

### 2020-10-11 STAT-paper-template/APA/fertile.tex
back to original tex file (not hard coded)

\caption{\label{tab:list-of-checks}Table illustrating the list of check available in fertile. }
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright\arraybackslash}p{4in}}
\toprule
Check & Functionality\\
\midrule
\cellcolor{gray!6}{has\_proj\_root()} & \cellcolor{gray!6}{Checks to make sure a single .Rproj file is found in the root directory of the project.}\\
has\_no\_nested\_proj\_root() & Checks to make sure there are no nested .Rproj files in subfolders of the project.\\
\cellcolor{gray!6}{has\_clear\_build\_chain()} & \cellcolor{gray!6}{Looks for indication of a clear order in which to run R scripts.}\\
has\_tidy\_[media/images/code/raw\_data/data/scripts]() & There are six different 'has\_tidy\_...' functions. Each checks to make sure that no files of its given type (images, code, data, etc.) are located in the root directory of the project\\
\cellcolor{gray!6}{has\_only\_used\_files()} & \cellcolor{gray!6}{Ensures that all files located in the project directory are being referenced or created by other files in the project.}\\
\addlinespace
has\_readme() & Checks to make sure there is a README file in the root directory.\\
\cellcolor{gray!6}{has\_well\_commented\_code()} & \cellcolor{gray!6}{Checks to ensure that all code files contain an adequate number of comments (>10\% of lines).}\\
has\_no\_absolute\_paths() & Checks to make sure that no absolute paths are referenced in code.\\
\cellcolor{gray!6}{has\_only\_portable\_paths()} & \cellcolor{gray!6}{Checks to make sure that no paths in code lead outside the project directory.}\\
has\_no\_randomness() & Checks to make sure code does not contain uncontrolled randomness.\\
\addlinespace
\cellcolor{gray!6}{has\_no\_lint()} & \cellcolor{gray!6}{Examines code to determine whether it conforms to 'tidy' style guide recommendations.}\\
\bottomrule
\end{tabu}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{log_report}\hlstd{()}
\end{alltt}
\begin{verbatim}
## # A tibble: 5 x 4
##   path         path_abs                             func     timestamp          
##   <chr>        <chr>                                <chr>    <dttm>             
## 1 package:pur~ <NA>                                 base::l~ 2020-10-11 15:10:40
## 2 package:for~ <NA>                                 base::l~ 2020-10-11 15:10:40
## 3 Seed Before  <NA>                                 14       2020-10-11 15:10:40
## 4 project_mic~ /Users/audreybertin/Documents/ferti~ readr::~ 2020-10-11 15:10:40
## 5 Seed After   <NA>                                 28       2020-10-11 15:10:40
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fertile}\hlopt{::}\hlstd{read_csv}
\end{alltt}
\begin{verbatim}
## function(file, ...) {
## 
##   if (interactive_log_on()) {
##     if (Sys.getenv("FERTILE_RENDER_MODE") == TRUE){
##       log_push('Seed Before', .Random.seed[2])
##     }
## 
##     log_push(file, "readr::read_csv")
## 
##     check_path_safe(file, ... = "readr::read_csv")
## 
##     data <- readr::read_csv(file, ...)
## 
##     if (Sys.getenv("FERTILE_RENDER_MODE") == TRUE){
##       log_push('Seed After', .Random.seed[2])
##     }
## 
##     return (data)
##   }
## }
## <bytecode: 0x7f9a68cb9468>
## <environment: namespace:fertile>
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{proj_dir}
\end{alltt}
\begin{verbatim}
## [1] "project_miceps"
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(proj_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## project_miceps/Blot_data_updated.csv   project_miceps/CS_data_redone.csv      
## project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\begin{alltt}
\hlstd{temp_dir} \hlkwb{<-} \hlkwd{sandbox}\hlstd{(proj_dir)}
\hlstd{temp_dir}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/Rtmpz372mQ/project_miceps
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(temp_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/Rtmpz372mQ/project_miceps/Blot_data_updated.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/Rtmpz372mQ/project_miceps/CS_data_redone.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/Rtmpz372mQ/project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

\caption{\label{tab:list-of-checks}Table illustrating the list of check available in fertile. }
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright\arraybackslash}p{4in}}
\toprule
Check & Functionality\\
\midrule
\cellcolor{gray!6}{has\_proj\_root()} & \cellcolor{gray!6}{Checks to make sure a single .Rproj file is found in the root directory of the project.}\\
has\_no\_nested\_proj\_root() & Checks to make sure there are no nested .Rproj files in subfolders of the project.\\
\cellcolor{gray!6}{has\_clear\_build\_chain()} & \cellcolor{gray!6}{Looks for indication of a clear order in which to run R scripts.}\\
has\_tidy\_[media/images/code/raw\_data/data/scripts]() & There are six different 'has\_tidy\_*()' functions. Each checks to make sure that no files of its given type (images, code, data, etc.) are located in the root directory of the project\\
\cellcolor{gray!6}{has\_only\_used\_files()} & \cellcolor{gray!6}{Ensures that all files located in the project directory are being referenced or created by other files in the project.}\\
\addlinespace
has\_readme() & Checks to make sure there is a README file in the root directory.\\
\cellcolor{gray!6}{has\_well\_commented\_code()} & \cellcolor{gray!6}{Checks to ensure that all code files contain an adequate number of comments (>10\% of lines).}\\
has\_no\_absolute\_paths() & Checks to make sure that no absolute paths are referenced in code.\\
\cellcolor{gray!6}{has\_only\_portable\_paths()} & \cellcolor{gray!6}{Checks to make sure that no paths in code lead outside the project directory.}\\
has\_no\_randomness() & Checks to make sure code does not contain uncontrolled randomness.\\
\addlinespace
\cellcolor{gray!6}{has\_no\_lint()} & \cellcolor{gray!6}{Examines code to determine whether it conforms to 'tidy' style guide recommendations.}\\
\bottomrule
\end{tabu}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{log_report}\hlstd{()}
\end{alltt}
\begin{verbatim}
## # A tibble: 5 x 4
##   path         path_abs                             func     timestamp          
##   <chr>        <chr>                                <chr>    <dttm>             
## 1 package:pur~ <NA>                                 base::l~ 2020-10-11 15:12:26
## 2 package:for~ <NA>                                 base::l~ 2020-10-11 15:12:26
## 3 Seed Before  <NA>                                 21       2020-10-11 15:12:26
## 4 project_mic~ /Users/audreybertin/Documents/ferti~ readr::~ 2020-10-11 15:12:26
## 5 Seed After   <NA>                                 35       2020-10-11 15:12:26
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fertile}\hlopt{::}\hlstd{read_csv}
\end{alltt}
\begin{verbatim}
## function(file, ...) {
## 
##   if (interactive_log_on()) {
##     if (Sys.getenv("FERTILE_RENDER_MODE") == TRUE){
##       log_push('Seed Before', .Random.seed[2])
##     }
## 
##     log_push(file, "readr::read_csv")
## 
##     check_path_safe(file, ... = "readr::read_csv")
## 
##     data <- readr::read_csv(file, ...)
## 
##     if (Sys.getenv("FERTILE_RENDER_MODE") == TRUE){
##       log_push('Seed After', .Random.seed[2])
##     }
## 
##     return (data)
##   }
## }
## <bytecode: 0x7fb05e74f770>
## <environment: namespace:fertile>
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{proj_dir}
\end{alltt}
\begin{verbatim}
## [1] "project_miceps"
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(proj_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## project_miceps/Blot_data_updated.csv   project_miceps/CS_data_redone.csv      
## project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\begin{alltt}
\hlstd{temp_dir} \hlkwb{<-} \hlkwd{sandbox}\hlstd{(proj_dir)}
\hlstd{temp_dir}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/Rtmpo24pt6/project_miceps
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(temp_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/Rtmpo24pt6/project_miceps/Blot_data_updated.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/Rtmpo24pt6/project_miceps/CS_data_redone.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/Rtmpo24pt6/project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\end{kframe}
\end{knitrout}
